Analyzing Crime Trends in Toronto: Insights from the Police Annual Statistical Report

### 2024-09-25 paper/paper.qmd
new

According to @fig-Crimes_by_Year,

>>>>

According to @fig-Crimes_by_Year，There was a sharp increase in crimes against property in 2023, reaching the highest number of incidents reported during the 2014-2023 period, with over 100,000 incidents. Crimes against the person maintained a relatively stable trend from 2014 to 2023, consistently reporting between 20,000 and 25,000 incidents annually. Traffic-related criminal code violations showed a decline from 2018, especially during 2020, where the number of reported incidents dropped below 15,000. Other categories, including "Controlled Drugs and Substances Act" and "Other Federal Statute Violations", remained consistently low over the years, each with less than 5,000 incidents reported annually.

## Crime Types by Division
Different divisions across Toronto report varying types of crimes. Divisions located in more urbanized areas, show higher concentrations of property crimes, such as auto theft and break-ins. At the same time, suburban areas report a higher frequency of violent crimes.

crime_by_division_plot <- analysis_data %>%
  group_by(division_name, crime_subtype) %>%
  summarise(total_incidents = sum(incidents_reported, na.rm = TRUE)) # Summing incidents per division and crime type
```

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-Crimes_by_Div
#| fig-cap: Crimes by Division and Crime Type

## Create a bar chart comparing crime types and incidents by division
crime_by_division_plot %>% 
  ggplot(aes(y = reorder(division_name, -total_incidents), x = total_incidents, fill = crime_subtype)) +
  geom_bar(stat = "identity", position = "dodge") +  # Using a bar chart for comparison
  labs(
    title = "Crime Incidents by Division and Crime Type in Toronto",
    y = "Division",
    x = "Total Incidents",
    fill = "Crime Type"
  ) #+
 # theme_minimal()  # Minimal theme for clean visuals
